### 2020-03-17 slides/preface.tex
Lunch w/ Ashwin. Done to P1-questions.
done with numerics (perhaps)
modified the numerics a bit
some modification

\begin{longtable}[]{@{}rl@{}}
  \toprule
  \endhead
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Respondent:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Zhouyang Ge\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Titel:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Droppinteraktioner och suspensionsflöden\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Handledare:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Prof.~Luca Brandt\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Asso.~Prof.~Outi Tammisola\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Fakultetsopponent:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Asso.~Prof.~Fran\c{c}ois Gallaire, École polytechnique fédérale de Lausanne, Schweiz\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Betygsnämnd:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Dr.~Elisabeth Lemaire, Institut de Physique de Nice, Frankrike\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Dr.~Martin Trulsson, Lund Universitet, Sverige\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Dr.~Gustaf M\aa rtensson, Mycronic AB, Sverige\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Ordförande:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Prof.~Fredrik Lundell\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Sponsorer:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    EU Horizon 2020 (MICROFLUSA), VR\strut
  \end{minipage}\tabularnewline
  \bottomrule
\end{longtable}
\end{frame}

\begin{frame}[plain]{Procedure}
\protect\hypertarget{procedure}{}
\begin{itemize}
\item
  \textbf{The respondent will present his thesis}
  \medskip
\item
  \textbf{The opponent will discuss the thesis}
  \medskip
\item
  \textbf{The grading committee will ask questions}
  \medskip
\item
  \textbf{The audience may ask questions}
  \medskip
\item
  \textbf{The public part of the defence will be closed}
  \medskip
\item
  \textbf{The result will be announced at Osquars Backe 18, floor 6}
\end{itemize}
\end{frame}

>>>>

\begin{longtable}[]{@{}rl@{}}
  \toprule
  \endhead
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Ordförande:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Prof.~Fredrik Lundell\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Respondent:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Zhouyang Ge\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Titel:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Droppinteraktioner och suspensionsflöden\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Handledare:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Prof.~Luca Brandt\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Assoc.~Prof.~Outi Tammisola\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Fakultetsopponent:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Assoc.~Prof.~Fran\c{c}ois Gallaire, École polytechnique fédérale de Lausanne, Schweiz\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Betygsnämnd:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Dr.~Elisabeth Lemaire, Institut de Physique de Nice, CNRS, Frankrike\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Assoc.~Prof.~Martin Trulsson, Lund Universitet, Sverige\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Dr.~Gustaf M\aa rtensson, Mycronic AB, Sverige\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Ersättare:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Prof.~Shervin Bagheri, KTH, Sverige\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Sponsorer:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    EU Horizon 2020 (MICROFLUSA)\strut
  \end{minipage}\tabularnewline
  \bottomrule
\end{longtable}
\end{frame}

\begin{frame}[plain]{Procedure}
\protect\hypertarget{procedure}{}
\begin{itemize}
\item
  \textbf{The respondent will present the thesis}
  \medskip
\item
  \textbf{The opponent will discuss the thesis}
  \medskip
\item
  \textbf{The grading committee will ask questions}
  \medskip
\item
  \textbf{The audience may ask questions}
  \medskip
\item
  \textbf{The public part of the defence will be closed}
  \medskip
\item
  \textbf{The result will be announced at Osquars Backe 18, floor 6}
\end{itemize}
\end{frame}
